%-------------------------
% Resume in Latex
% Author : Kartik Agarwal
% Based off of: https://github.com/kartikag01/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand\+{\raisebox{0.25ex}{+}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Kartik Agarwal} \\ \vspace{1pt}
    \small +91-8077976962 $|$ \href{mailto:x@x.com}{\underline{kartikagarwal01@gmail.com}} $|$ 
    \href{https://linkedin.com/in/kartikag01}{\underline{linkedin.com/in/kartikag01}} $|$
    \href{https://github.com/kartikag01}{\underline{github.com/kartikag01}}
\end{center}

%-----------SUMMARY-----------

%-----------SUMMARY ENDS-----------
\section{Summary}
Passionate Software Engineer with 8 years of experience and talent for creating intuitive and high-performing web applications. I have experience in leading startups, where I have built large scale products and features from scratch.
I am also a co-organizer and Speaker @reactdelhincr and have given more than 10 workshops and talks.

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://partsavatar.ca/}{PartsAvatar} - Technical Team Lead}{September 2019 -- Present}
      {Canada’s leading autoparts Ecommerce Platform}{Gurgaon}
      \resumeItemListStart
      \resumeItem{Responsible for the Storefront Web, CMS App and CS Portal.}
      
\resumeItem{Implemented server-side rendering (SSR) in Next.js, leading to increase in search engine visibility.}
\resumeItem{Built CS Chat Routing app, integrated with Freshchat, Rasa Bot and Chat Client via Sockets, webhook in Node.js}
\resumeItem{Improved Core Web Vitals metrics score to 85\+ using CLS, LCP, JS Optimisation.}
\resumeItem{Rebuild Home Page, Checkout, Product Pages, Category Pages.}
\resumeItem{Created many other new set of pages ProductLine, MakeTierX, MakeModelTier with interlinking them.}


\resumeItem{Boosted CDN efficiency, elevating hit rates from 3\% to 45\% for faster content delivery.}

% \resumeItem{Significantly improved Website Performance, UI/UX.}
% \resumeItem{Responsible for mentoring and day-to-day supervision of 3-5 front-end developers.}

\resumeItem{Teamed up with UX designers to enhance designs, came up with new features and idea for the business.}

\resumeItem{Setup Automation Testing using Cypress and conducted Unit testing in testing-library and Snapshot testing.}

\resumeItem{Done seamless deployments initially with Serverless and later with ECS.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
   % \resumeSubSubheading
   %  {Sr. Software Developer}{September 2019 - September 2021}
   %  \resumeItemListStart
   %     \resumeItem{Apache Beam}
   %       {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
   %  \resumeItemListEnd
   % \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {\href{https://leena.ai/}{Leena.ai} - Frontend Lead}{Nov. 2018 -- Sept. 2019}
      {HR Tech Platform }{Gurgaon}
      \resumeItemListStart
\resumeItem{Created Employee Engagement, HR Ticketing System from scratch.}
\resumeItem{Designed Customizable Elements, Components UI Library, which is used in typeforms and other systems.}
\resumeItem{Rebuild HR Help Desk Chat App with new features and support for IE 11.}
\resumeItem{Implemented ESLint, CSS modules, code splitting, and project starter kit.}

    \resumeItemListEnd

    \resumeSubheading
      {Practo - Frontend Engineer}{March 2018 -- November 2018}
      { Health Tech}{Banglore}
      \resumeItemListStart
\resumeItem{Worked on Hospital Management System.}
\resumeItem{Developed Triage and Initial Assessment by Custom Form based Modules.}
\resumeItem{Done Snapshot and Unit testing of Components and Sagas.}
\resumeItem{Fixed critical bugs in the Registration and Insurance module.}
      \resumeItemListEnd

    \resumeSubheading
      {Workex - Sr. Software Developer}{March 2017 -- Feb 2018}
      {Social Platform for Blue collar jobs}{Banglore}
      \resumeItemListStart
      \resumeItem{Build ATS with Chat module in Node.js and Express using MongoDB from scratch.}
\resumeItem{Created Admin BE and UI for Chat Master, Dashboards, Data View and Control Panel.}
\resumeItem{POC on User Feed generating system on multiple modules like Jobs, Courses, Attendance, News, Work etc.}
      \resumeItemListEnd


      \resumeSubheading
      {Zuppit  - Software Developer}{Feb 2016 -- Feb 2017}
      {Article Summary AI App}{Gurgaon}
      \resumeItemListStart
      \resumeItem{Developed DIY Chatbot Development Platform UI with custom AI Models, API and custom Bot Flows.}
\resumeItem{Added Cricket Live Score Feature in Android App (News Summary Android App)}

      \resumeItemListEnd

  \resumeSubHeadingListEnd



%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {B.Tech in Computer Science}{June. 2012 -- June 2016}
      {ABES Engineering College, Ghaziabad}{CGPA - 8.0}
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, Typescript, Nodejs, ES6, Webpack, HTML, CSS, Postgres, MongoDB.} \\
     \textbf{Frameworks}{: Reactjs, Nextjs, Redux, Express, Prisma, Cypress, Jest.} \\
     \textbf{Others}{: Web Preformance, CSR, SSR, WebSockets, Jenkins, AWS, Git, Jira, GA4, Google Search Console.} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
